Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-18 paper/paper.tex
pass on mining tests

To mine tests from the textual descriptions we proceeded as
follows. First, we broke the text describing the issue in paragraphs
and used a binary classifier to label each paragraph as ``code'' or
``not code''. Then, based on that information, we merged consecutive
paragraphs labeled as ``code'' and used a \js\ parser to check
well-formedness of the corresponding code fragment. Using that method
we were able to retrieve a total of \Fix{XX} files (\jsc{}=\Fix{XX},
\veight{}=\Fix{XX}, \smonkey{}=\Fix{XX}). All those files were
included in Table~\ref{tab:test-suites}.  Surprisingly, we did not
find a public classifier to solve the problem above. For space, we
summarize the solution that worked the best in the following. The
classifier that performed best for this case uses
a standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain
  what this ``Embeddings'' thing does at a high-level. Also, if this
  stuff exists why we did not find a solution off-the-shelf?} that
builds on a neural net~\Fix{cite} to keep a dictionary of words and the
similarity distance among them\Mar{but we are talking about
  sentences. how does it go from words to sentences? Note that many
  words from the ``code'' vocabulary are from English!}. In more
detail, the classification model uses a Convolutional Neural
Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
  meaning for each layer?} and has been trained and evaluated using a
dataset with 25K samples of English paragraphs and 25K snippets of
\js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
evaluate the model and obtained a predicted accuracy of
\Fix{98\%}. This classifier is publicly available from our website as
a separate component.

>>>>

To mine tests from the textual descriptions we proceeded as
follows. First, we broke the text describing the issue in paragraphs
and used a binary classifier to label each paragraph as ``code'' or
``not code''. Then, based on that information, we merged consecutive
paragraphs labeled as ``code'' and used a \js\ parser to check
well-formedness of the corresponding code fragment. Using that method
we were able to retrieve a total of \Fix{XX} files (\jsc{}=\Fix{XX},
\veight{}=\Fix{XX}, \smonkey{}=\Fix{XX}). All those files were
included in Table~\ref{tab:test-suites}.  Surprisingly, we did not
find a public classifier to solve the problem above. 
\Igor{
For space, we summarize the solution that worked the best in the following. 
We used a standard Embeddings NLP word2vec \cite{kusner2015word}
to get the relationship between sentences and as feature extractor to 
feed the neural network (NN). 
Embedding is a technique that uses a neural network to encoding data 
in a vector of fixed length, mainly, categorical data. 
In this context, embedding was used following the method skip-gram whose 
the purpose is given a word, predict the neighbors words.
The model has been trained and evaluated using a
dataset with 25K samples of English paragraphs and 25K snippets of
\js{}. Devido a quantidade de amostras ser relativamente grande, 
utilizamos a validação durante cada epoch no treinamento and 
obtained a predicted accuracy of \Fix{98\%}.
This classifier is publicly available from our website as
a separate component.
}
\Comment{
For space, we
summarize the solution that worked the best in the following. The
classifier that performed best for this case uses
a standard Embeddings NLP technique~\Fix{cite}\Mar{needs to explain
  what this ``Embeddings'' thing does at a high-level. Also, if this
  stuff exists why we did not find a solution off-the-shelf?} that
builds on a neural net~\Fix{cite} to keep a dictionary of words and the
similarity distance among them\Mar{but we are talking about
  sentences. how does it go from words to sentences? Note that many
  words from the ``code'' vocabulary are from English!}. In more
detail, the classification model uses a Convolutional Neural
Network~\Fix{cite} classifier with two layers\Mar{why two? is there a
  meaning for each layer?} and has been trained and evaluated using a
dataset with 25K samples of English paragraphs and 25K snippets of
\js{}. We ran a standard \Fix{X}-repeated 10-fold cross validation to
evaluate the model and obtained a predicted accuracy of
\Fix{98\%}. This classifier is publicly available from our website as
a separate component.
}
